\mytitle

### 2015-07-30 MSc_diss.tex
New figure in section about model validation

\begin{table} % model setup: VOCs
\caption{Model setup: VOCs concentrations (ppb)}\label{tab:setupVOCs}
\centering
\begin{tabular}{ccccccccc}
\hline
Experiment number & $CH_4$ & $C_2H_6$ & $C_3H_8$ & $nC_4H_{10}$ & $iC_4H_{10}$ & $nC_5H_{12}$ & $iC_5H_{12}$ \\
\hline
A  & 1780 &	0.620 &	0.100 &	0.050 &	0.250 &	0.250 &	0.250 \\
B  & 1807 &	1.258 &	0.390 &	0.245 &	0.325 &	0.275 &	0.425 \\
C  & 1834 &	1.896 &	0.680 &	0.440 &	0.400 &	0.300 &	0.600 \\
D  & 1861 &	2.534 &	0.970 &	0.635 &	0.475 &	0.325 &	0.775 \\
E  & 1888 &	3.172 &	1.260 &	0.830 &	0.550 &	0.350 &	0.950 \\
F  & 1915 &	3.810 &	1.550 &	1.025 &	0.625 &	0.375 &	1.125 \\
G  & 1942 &	4.448 &	1.840 &	1.220 &	0.700 &	0.400 &	1.300 \\
H  & 1969 &	5.086 &	2.130 &	1.415 &	0.775 &	0.425 &	1.475 \\
I  & 1996 &	5.724 &	2.420 &	1.610 &	0.850 &	0.450 &	1.650 \\
J  & 2023 &	6.362 &	2.710 &	1.805 &	0.925 &	0.475 &	1.825 \\
K  & 2050 &	7.000 &	3.000 &	2.000 &	1.000 &	0.500 &	2.000 \\
\hline
\end{tabular}
\end{table}
\subsection{Model performance}
Due to imperfection of the chemical mechanism time evolution of species concentrations given by the model does not completely agree with the photochemical theory, but reproduces it to some extent. Figure \ref{fig:model_validation} shows an example of output from the model, namely the changes in mixing ratios of the main species within 24-hours of simulation time under contrasting $NO_x$ and $VOCs$ conditions. The values shown in Figure \ref{fig:model_validation} have been justified from the theoretical point of view and also compared with those derived from the Atmospheric Chemistry Learner's Box Model (ACLBM, http://guille.zicer.uea.ac.uk/ACLBM). ACLBM is an on-line box model for atmospheric chemistry developed by Prof. Roland von Glasow (University of East Anglia) that allows the selection of several chemical reaction mechanisms, choice of initial concentrations and emission fluxes. For comparison with our modelling data the ACLBM was set up and initialized with values from Tables \ref{tab:setupO3CO}, \ref{tab:setupNOx} and \ref{tab:setupVOCs}, and the '$O_3$-$NO_x$-$CO$-$CH_4$' chemical mechanism was chosen as it is the closest version of the chemical mechanism available in the ACLBM to our model.

@@

\begin{figure} % Sillman1999withdotsline and netO3rate
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{{./pics/Sillman1999_Fig1_adapted_withdotssquare}.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, solid lines) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) for mean summer daytime meteorology and clear skies. The solid lines represent production rates of 1, 2.5, 5, 10, 15, 20 and 30 ppb/h. Adapted from \citep{Sillman1999}.}\label{fig:Sillman1999}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_withINORG_ppbC.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) in the first modelling experiment with alkyl nitrate chemistry switched off combined with an additional run with inorganic chemistry only (i.e. the only $VOC$ is $CO$).}\label{fig:noAN_netO3_rate}
\end{minipage}
\end{figure}

@@

\section{Results} \label{sec:res}
\begin{figure}[h] % allAN_netO3_rate
\includegraphics[width=\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3_rate.png}
\caption{allAN, netO3 rate}\label{fig:allAN_netO3_rate}
\end{figure}

>>>>

\begin{table} % model setup: VOCs
\caption{Model setup: VOCs concentrations (ppb)}\label{tab:setupVOCs}
\centering
\begin{tabular}{ccccccccc}
\hline
Experiment number & $CH_4$ & $C_2H_6$ & $C_3H_8$ & $nC_4H_{10}$ & $iC_4H_{10}$ & $nC_5H_{12}$ & $iC_5H_{12}$ \\
\hline
A  & 1780 &	0.620 &	0.100 &	0.050 &	0.250 &	0.250 &	0.250 \\
B  & 1807 &	1.258 &	0.390 &	0.245 &	0.325 &	0.275 &	0.425 \\
C  & 1834 &	1.896 &	0.680 &	0.440 &	0.400 &	0.300 &	0.600 \\
D  & 1861 &	2.534 &	0.970 &	0.635 &	0.475 &	0.325 &	0.775 \\
E  & 1888 &	3.172 &	1.260 &	0.830 &	0.550 &	0.350 &	0.950 \\
F  & 1915 &	3.810 &	1.550 &	1.025 &	0.625 &	0.375 &	1.125 \\
G  & 1942 &	4.448 &	1.840 &	1.220 &	0.700 &	0.400 &	1.300 \\
H  & 1969 &	5.086 &	2.130 &	1.415 &	0.775 &	0.425 &	1.475 \\
I  & 1996 &	5.724 &	2.420 &	1.610 &	0.850 &	0.450 &	1.650 \\
J  & 2023 &	6.362 &	2.710 &	1.805 &	0.925 &	0.475 &	1.825 \\
K  & 2050 &	7.000 &	3.000 &	2.000 &	1.000 &	0.500 &	2.000 \\
\hline
\end{tabular}
\end{table}
\subsection{Model performance}
Due to imperfection of the chemical mechanism time evolution of species concentrations given by the model does not completely agree with the photochemical theory, but reproduces it to some extent. Figure \ref{fig:model_validation} shows an example of output from the model, namely the changes in mixing ratios of the main species within 24-hours of simulation time under contrasting $NO_x$ and $VOCs$ conditions. The values shown in Figure \ref{fig:model_validation} have been justified from the theoretical point of view and also compared with those derived from the Atmospheric Chemistry Learner's Box Model (ACLBM, http://guille.uea.ac.uk/ACLBM/). ACLBM is an on-line box model for atmospheric chemistry developed by Prof. Roland von Glasow (University of East Anglia) that allows the selection of several chemical reaction mechanisms, choice of initial concentrations and emission fluxes. For comparison with our modelling data the ACLBM was set up and initialized with values from Tables \ref{tab:setupO3CO}, \ref{tab:setupNOx} and \ref{tab:setupVOCs}, and the '$O_3$-$NO_x$-$CO$-$CH_4$' chemical mechanism was chosen as it is the closest version of the chemical mechanism available in the ACLBM to our model.

@@

\begin{figure} % Sillman1999withdotsline and netO3rate_withINORG_NOx_1ppb_100ppb
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{{./pics/Sillman1999_Fig1_adapted_withdotssquare}.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, solid lines) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) for mean summer daytime meteorology and clear skies. The solid lines represent production rates of 1, 2.5, 5, 10, 15, 20 and 30 ppb/h. Adapted from \citep{Sillman1999}.}\label{fig:Sillman1999}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_withINORG_NOx_1ppb_100ppb.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) in the first modelling experiment with alkyl nitrate chemistry switched off combined with an additional run with inorganic chemistry only (i.e. the only $VOC$ is $CO$).}\label{fig:noAN_netO3_rate}
\end{minipage}
\end{figure}

Rewrite!

@@

\section{Results} \label{sec:res}

%\begin{figure}[h] % allAN_netO3_rate
%\includegraphics[width=\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3_rate.png}
%\caption{allAN, netO3 rate}\label{fig:allAN_netO3_rate}
%\end{figure}
